% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Baoxian Zhang}

\basicInfo{
  \email{baoxianzhit@gmail.com} \textperiodcentered\ 
  \phone{(+86) 158-1553-5057} % \textperiodcentered\ 
  \github[baoxianzhang]{https://github.com/baoxianzhang}
  % \linkedin[baoxian zhang]{https://www.linkedin.com/in/baoxianz-zhang}
  }
 \section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Harbin Institute of Technology}}{Sep. 2011 -- Jan. 2014}
\textit{Master student} in Control Science and Engineering
\datedsubsection{\textbf{HeFei University of Technology}}{Sep. 2007 -- Jul. 2011}
\textit{B.S.} in Vehicle Engineering

\section{\faUsers\ Experience}
\datedsubsection{\textbf{MOLMC Inc.}}{Jul. 2015 -- Dec. 2016}
\role{Algorithm Engineer \& Embedded Software Engineer}{}
Engaged in optical localization algorithm, embedded software development.
\begin{itemize}
  \item Implemented optical localization data acquistion and the localization algorithm.
  \item Implemented four kinds of products development and testing.
  \item Familiar with STM32, ESP8266, ESP32 and OpenWRT.
\end{itemize}

\datedsubsection{\textbf{Guangdong Institute of Automation}}{Mar. 2014 -- Jul. 2015}
\role{Research Assistant}{}
Engaged in attitude algorithm and sensor calibration Of UAV.
\begin{itemize}
  \item Calibrated accelerometer, gyroscope and magnetometer, the sensor
    precision was improved.
  \item Calculated UAV attitude by multi-sensor fusion using Kalman algorithm.  
\end{itemize}

\datedsubsection{\textbf{Harbin Institute of Technology}}{Sep. 2011 -- Jan. 2014}
\role{Master Student}{}
The simultaneous localization and mapping based on multi-sensor fusion.
\begin{itemize}
  \item Extracted color and depth information of Kinect and Extracted features
    of the color image using OpenCV to loacalize the robot.
  \item Solved the map fusion of 2D grid map and 3D point cloud map. Used the
    AMCL localization method to align Map of Multi-robot SLAM with Heterogenous Sensors.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C, C++, Python
  \item Platform: Linux, Windows
  \item Tools: Emacs, Vim
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{Harbin Institute of Technology}, The special awawd and the first prize}{2011 -- 2014}
\datedline{\textit{HeFei University of Technology}, National scholarship and the
  first prize} {2007 -- 2011}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  % \item Blog: http://your.blog.me
  % \item GitHub: https://github.com/username
  \item Languages: English (CET-6) 
  \item The deriver's license (C1)
  \item Badminton, Table Tennis, Basketball
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
